### 2020-04-21 final_report/data.tex
add table of slice feature assignments

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{l|llll}
		\toprule
		{} & Parameter name & Type & Domain & Description\\
		\midrule
		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		& Breeder fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & TODO\\
		& Breeder \isotope[6]{Li} enrichment fraction & Continuous & $[0,1]$ & {}\\
		& Breeder material & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
		& Breeder packing fraction & Continuous & $[0,1]$ & {}\\
		& Coolant fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		& Multiplier fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Multiplier material & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
		& Multiplier packing fraction & Continuous & $[0,1]$ & {}\\
		& Structural fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		& Thickness & Continuous & $[0,500]$ & {}\\
		\midrule
		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
		& Armour fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Armour material & Discrete & $\{\text{tungsten}\}$ & {}\\
		& Coolant fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		& Structural fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		& Thickness & Continuous & $[0,20]$ & {}\\
		\bottomrule
		\end{tabular}
	}
	\caption{Input parameters supplied to the MC TBR simulation in alphabetical
		order. Fractions marked with superscripts\textsuperscript{\textdagger
		\textdaggerdbl} are independently required to sum to one.}
	\label{tbl:params}
\end{table}

@@

Skipping run zero, which was performed using older, fundamentally different
version of the MC TBR software, and was thus treated as a technical
proof-of-concept, we generated the total of~\num{900000} samples in two runs.
While the first run featured fully uniform sampling of the unrestricted feature
space, the second run used more elaborate strategy. Interested in further study
of relationships between discrete and continuous features, we selected four
assignments of discrete features and fixed them for all points, effectively
slicing the feature space into four corresponding subspaces. In order to achieve
comparability between these \textit{slices}, the remaining unassigned features
were sampled only in the first slice, and reused in the other three.

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{l|lllll}
		\toprule
		{} & Parameter name & Acronym & Type & Domain & Description\\
		\midrule
		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		   & Breeder fraction\textsuperscript{\textdagger} & BBF & Continuous & $[0,1]$ & TODO\\
		   & Breeder \isotope[6]{Li} enrichment fraction & BBLEF & Continuous & $[0,1]$ & {}\\
		   & Breeder material & BBM & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
		   & Breeder packing fraction & BBPF & Continuous & $[0,1]$ & {}\\
		   & Coolant fraction\textsuperscript{\textdagger} & BCF & Continuous & $[0,1]$ & {}\\
		   & Coolant material & BCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		   & Multiplier fraction\textsuperscript{\textdagger} & BMF & Continuous & $[0,1]$ & {}\\
		   & Multiplier material & BMM & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
		   & Multiplier packing fraction & BMPF & Continuous & $[0,1]$ & {}\\
		   & Structural fraction\textsuperscript{\textdagger} & BSF & Continuous & $[0,1]$ & {}\\
		   & Structural material & BSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		   & Thickness & BT & Continuous & $[0,500]$ & {}\\
		\midrule
		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
		   & Armour fraction\textsuperscript{\textdaggerdbl} & FAF & Continuous & $[0,1]$ & {}\\
		   & Armour material & FAM & Discrete & $\{\text{tungsten}\}$ & {}\\
		   & Coolant fraction\textsuperscript{\textdaggerdbl} & FCF & Continuous & $[0,1]$ & {}\\
		   & Coolant material & FCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		   & Structural fraction\textsuperscript{\textdaggerdbl} & FSF & Continuous & $[0,1]$ & {}\\
		   & Structural material & FSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		   & Thickness & FT & Continuous & $[0,20]$ & {}\\
		\bottomrule
		\end{tabular}
	}
	\caption{Input parameters supplied to the MC TBR simulation in alphabetical
		order. Fractions marked with superscripts\textsuperscript{\textdagger
		\textdaggerdbl} are independently required to sum to one.}
	\label{tbl:params}
\end{table}

@@

Skipping run zero, which was performed using older, fundamentally different
version of the MC TBR software, and was thus treated as a technical
proof-of-concept, we generated the total of~\num{900000} samples in two runs.
While the first run featured fully uniform sampling of the unrestricted feature
space, the second run used more elaborate strategy. Interested in further study
of relationships between discrete and continuous features, we selected four
assignments of discrete features (listed in~\cref{tbl:slices}) and fixed them
for all points, effectively slicing the feature space into four corresponding
subspaces. In order to achieve comparability between these \textit{slices}, the
remaining unassigned features were uniformly sampled only in the first slice,
and reused in the other three.

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{r|lllllll}
		\toprule
		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
		Jobs & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
		\midrule
		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		\bottomrule
		\end{tabular}
	}
	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
	\label{tbl:slices}
\end{table}
